\section{$p$-adic Integration on Modular Curves}

\subsection{Motivation}

\begin{frame}{Motivation}
\begin{theorem}[Faltings '83]
Let $X/K$ be a nice \footnote{smooth, projective, geometrically irreducible} curve of genus $g \geq 2$. Then the set of rational points $X(K)$ is finite.
\end{theorem} \pause
\begin{itemize}
\item Subsequent proofs by Vojta ('91), Faltings ('91) , Bombieri ('90), Lawrence-Venkatesh ('20) \pause
\item Uniformity bounds: Dmitrov-Gao-Habbeger ('21) , Betts-Corwin ('22), ...
\end{itemize}
\end{frame}

\begin{frame}{Motivation (cont.)}
\begin{theorem}[Chabauty '41]
Let $X$ be a nice curve of genus $g \geq 2$. Let $J$ be its Jacobian and $r:= rank(J(\QQ))$. If $r < g$, then $X(\QQ)$ is finite.
\end{theorem} \pause

\begin{theorem}[Coleman '85]
Suppose $r < g$ and $p > 2g$ prime of good reduction. Then

\[
|X(\QQ)| \leq |X(\FF_p)| + 2g -2 
\]

\pause In fact, one can compute a finite subset of $X(\QQ_p)$ containing $X(\QQ)$ in terms of $p$-adic line integrals of $1$-forms.
\end{theorem}
\end{frame}

\begin{frame}{Coleman integrals}
Suppose $X/\QQ_p$ is a nice curve with good reduction at a prime $p$. We can define a $p$-adic integral:

\[
\int_P^Q \omega \in \bar{\QQ}_p
\]

where $P,Q \in X(\bar{\QQ}_p), \omega \in H^0(X, \Omega^1)$. \pause These integrals satisfy many properties: linearity, additivity of endpoints, change of variables, FTC, etc.
\end{frame}

\begin{frame}{One crucial property}
If $P,Q$ reduce to the same point in $X(\bar{\FF}_p)$, the integral $\int_P^Q \omega$ becomes a \textit{tiny integral}:

\[
\int_P^Q \omega = \int_{t(P)}^{t(Q)} \omega(t) = \int_{t(P)}^{t(Q)} \sum a_i t^i dt = \sum \frac{a_i}{i+1} (t(Q)^{i+1} - t(P)^{i+1})
\]
\end{frame}


\begin{frame}{Chabauty-Coleman method}
Suppose $r < g$. Let $b \in X(\QQ)$ be a basepoint. Then

\[
\{ x \in X(\QQ_p): \int_b^x \omega = 0 \} \supseteq X(\QQ)
\]

along with Newton polygons and Mordell-Weil sieves would recover the set of rational points.

\end{frame}

\begin{frame}{Bottleneck}
If $P,Q$ lie in different residue discs, one would need to compute the action of Frobenius on the MW cohomology via Kedlaya's algorithm. \pause After that, one solves the following system of equations:

\[
\sum_j (M - I)_{ij}(\int_P^Q \omega_j) = f_i(P) - f_i(Q) - \int_P^{\phi(P)} \omega_i - \int_{\phi(Q)}^Q \omega_i
\]

where $\phi$ is the Frobenius map which acts on the differentials via $\phi^* \omega_i = df_i + \sum_j M_{ij}\omega_j$. \textbf{This relies on a model of the curve}.
\end{frame}


